The problem and promise of scale in multilayer animal social networks

### 2020-02-15 paper/manuscript.Rmd
add corresponding email

---
title: The problem and promise of scale in multilayer animal social networks
author: Alec L. Robitaille^1^, Quinn M.R. Webber^2^, Julie W. Turner^1^, Eric Vander Wal^1,2^
date: ^1^Department of Biology, Memorial University of Newfoundland, Canada; ^2^Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial University of Newfoundland
output:
  # github_document
  # bookdown::pdf_document2:
  #    number_sections: true
  bookdown::word_document2:
    reference_docx: template.docx
# bibliography: ../references/knitcite.bib
---

>>>>

---
title: The problem and promise of scale in multilayer animal social networks
author: Alec L. Robitaille^1\*^, Quinn M.R. Webber^2^, Julie W. Turner^1^, Eric Vander Wal^1,2^
date: |
  | ^1^Department of Biology, Memorial University of Newfoundland, Canada
  | ^2^Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial University of Newfoundland 
  | \*Corresponding author: Alec L. Robitaille (robit.alec@gmail.com)
output:
  # github_document
  bookdown::pdf_document2:
     number_sections: true
     toc: false
  # bookdown::word_document2:
  #   reference_docx: template.docx
bibliography: ../references/knitcite.bib
---
